It has been more than 8 years that I finished and handed in my diploma thesis and decided to continue with the Master's programme in ``Applied Economics'' at the University of Innsbruck. Back in 2011 I could have never imagined how much more I would learn again during the upcoming years and how many wonderful individuals would cross my way, become close friends and make the time throughout the Master's programme and beyond a unique period in my life. In particular, I want to thank Christian Aichmüller, Judith Santer, Nathan Harrold, Alban Zeiger, Rudolf Hakenschmidt, Katrin Findeisen, Sabrina Ronacher, Caro Poullain, Silvia Hribik and Bettina Lubach. \\ 
\\
With regard to my studies, I used the time to broaden and deepen my knowledge in Econometrics and Mathematics/Statistics, more generally. In this respect I want to thank Prof. Dr. Achim Zeileis, whose classes in Microeconometrics and Time Series Analysis allowed me to gain a deeper understanding of Econometric Analyses, Prof. Michael Pfaffermayr who introduced us to the more advanced parts of econometric theory, Prof. Dr. Janette Walde who held one of the very first classes in the Master's Programme (Mathematics for Economists) and Prof. Dr. Peter Wagner, who I met while attending classes at the Technical Faculty of our university. His courses in Mathematics 1 \& 2 and Probability Theory and Statistics were one of the best classes I have attended throughout my time at university.\\
I also had the chance to train my critical thinking in countless conversations with my fellow students that gave me very valuable insights on the Economics-discipline itself and the work we have ahead to advance in this field that is prone to so much controversy in academia and public discussions. I, especially, want to mention my dear friend Alban Zeiger that introduced me (and my fellow students) to the fantastic work of Heiner Flassbeck and his platform flassbeck-economics (which later changed its name into Makroskop). I definitely hope that we all can contribute to this mission that is ahead of us.\\
\\
Beginning with the summer term 2012 I also got the opportunity to gain my first teaching experiences by holding two seminars within the Bachelor's course ``Public Economics'' here at our university. This is all due to my friend Dr. Martin Gächter that had supported and accompanied me through many years already and I was sitting in his very office when suddenly a colleague dropped by, mentioning that the department of Public Finance is seeking teaching assistants for their seminars. And well, the rest is history.
\newpage
\thispagestyle{empty} %bewirk, dass die Striche oben wegfallen und, dass die Seitenzahl wegfällt.
I am very much indebted to Prof. Dr. Engelbert Theurl and Prof. Dr. Rupert Sausgruber for giving me the opportunity to prove my teaching abilities. It was a great chance for me that changed the course of many things to come. I am also for  my dear friend Christian Aichmüller that immediately thought of me when a tutoring position in Microeconomics opened up as well. The subsequent collaboration with Dr. Christoph Hauser was very fruitful and pleasant.\\
\\
The reason for me sitting down to write this thesis with a couple of years in between the last courses I had taken for this Master's degree are my eagerness to study Mathematics (which I did for two semesters from 2014 until 2015) and the opportunity to join the Austrian National Bank's Economic Studies Division as of July 2015 as a research assistant for half a year. I want to thank everyone that was part of my journey at the OeNB, in particular Esther Segalla. Beyond that I want to thank Martin Summer, Markus Knell, Helmut Elsinger, Helmut Stix, Graziella Hofbaur-Berlakovic, Walter Waschiczek, Dominik Stelzeneder, Lisa Kothmayr, Jun Chao Zhan, Anna-Camilla Drahonsky, Robert Köck and Ruth Fulterer as well as the amazing people I met at the Strudlhofgasse student home (in particular, Lisa Schweitzer, Ilka Lindner, Hamed Barzegar and Pascal Schwerin).  \\
\\
My next step after the internship was the European Central Bank which I joined in April 2016 and where I stayed for almost two years in the DG-Statistics. This time was incredibly challenging but also enriching both from a professional and a personal perspective due to my colleagues and the many great friendships I could make throughout this time. I want to mention in particular Francesca Gnecchi, Rocco Incardona, Matteo Paolo Pirone, Taja Sečnik, Simon Gollier, Laura Battalia, Nicolas Lemercier, Sara Thijs, Mattia Duma, Jörg Reddig, Sandrine Corvoisier, Peter Neudorfer, Riccardo Bonci, Gianluca Pallante, Jean-Marc Israel, Branchi Mariagnese, Marta Lopez Villa, Antonio Colangelo, Orestes Collazo Brananova, Catherine Ahsbahs, Alejandro Pica, Romana Peronaci, Alexandra-Iulia Chindea, Ioanna Kanioura, Julie Van Eeckhout, Me-Lie Yeh, Gemma Agostoni, Zeno Benetti, Damjan Strbac, Olgerd Unger, Darjan Divkovic, Bernadette Lauro, Krishanu Saha, Valeria Martone, Mirko de Giovanni, Sotirios Dimitrios Anagnostidis, Lyubomir Dilov, Nina Berghoff, Angelo Saponara, Johannes Micheler, Jürgen Herr and Sami Laiso.
\newpage
\thispagestyle{empty} %bewirk, dass die Striche oben wegfallen und, dass die Seitenzahl wegfällt.
Soon after my time at the ECB, I joined the QAS-Team at EY Germany and, at the time of writing, am closing my second year. I will forever be grateful for the opportunity Dr. Bernhard Hein and Dr. Martin Dörr have given me to join their family at EY. I met wonderful people and learned an incredible amount about credit risk, market risk and the many challenges of banking in the 21st century. Thank you all! And here's to many more years!