\newgeometry{left=30mm, right=30mm, top=50mm, bottom=50mm}
It has been more than five years now that I finished and handed in my diploma thesis and decided to continue with the Master's programme in "Applied Economics" at the University of Innsbruck. Back in 2011 I could have never imagined how much more I would learn again during the upcoming years and how many wonderful individuals would cross my way, become close friends and make the time throughout the Master's programme a unique period in my life. In particular I want to thank Christian Aichmüller, Judith Santer, Nathan Harrold, Alban Zeiger, Rudolf Hakenschmidt, Katrin Findeisen, Sabrina Ronacher, Caro Poullain, Silvia Hribik and Bettina Lubach. \\ 
\\
With regard to my studies, I used the time to broaden my knowledge in Econometrics and Mathematics and Statistics, more generally. In this respect I want to thank, in particular, Prof. Dr. Achim Zeileis, whose classes in Microeconometrics and Time Series Analysis I've been allowed to attend, Prof. Michael Pfaffermayr that introduced us to the more advanced parts of econometric theory, Prof. Dr. Janette Walde that introduced us to Mathematics for Economists and Prof. Dr. Peter Wagner, who I met while attending classes at the Technical Faculty of our university. His courses in Mathematics 1 \& 2 and Probability Theory and Statistics opened a door for me that had been closed way too long.\\
I also had the chance to train my critical thinking in countless conversations with my fellow students that gave me very valuable insights on the Economics-discipline itself and the work we have ahead to advance in this field that is prone to so much controversy in academia and public discussions. I definitely hope that we all can contribute to this mission that is ahead of us.\\
\\
Beginning with the summer term 2012 I also got the opportunity to gain my first teaching experiences by holding two seminars within the Bachelor's course "Public Economics" here at our university. This is all only due to my friend Dr. Martin Gächter that had supported and accompanied me through many years already and I was sitting in his very office when suddenly a colleague dropped by, mentioning that the department of Public Finance is seeking teaching assistants for their seminars. And well, the rest is history.
\newpage
I am very much indebted to Prof. Dr. Engelbert Theurl and Prof. Dr. Rupert Sausgruber for trusting me and giving me the opportunity to prove my teaching abilities. It was a great chance for me that changed the course of many things to come. I am also indebted to my dear friend Christian Aichmüller that immediately thought of me when a tutoring position in Microeconomics opened up as well. The subsequent collaboration with Dr. Christoph Hauser was very fruitful and pleasant.\\
\\
The reason for me sitting down to write this thesis with a couple of years in between the last courses I had taken for this Master's degree are my eagerness to study Mathematics (which I did for two semesters from 2014 until 2015) and the amazing opportunity to join the Austrian National Bank's Economic Studies Division as of July 2015 as a research assistant for half a year. I want to thank everyone that was part of my journey at the OeNB, in particular Esther Segalla, Markus Knell, Martin Summer, Helmut Elsinger, Helmut Stix, Graziella Hofbaur-Berlakovic, Walter Waschiczek, Dominik Stelzeneder, Lisa Kothmayr, Jun Chao Zhan, Anna-Camilla Drahonsky, Robert Köck and Ruth Fulterer as well as my amazing people I met at the Strudlhofgasse student home (in particular, Lisa Schweitzer, Ilka Lindner, Hamed Barzegar and Pascal Schwerin).  \\
\\
I could have never imagined that my next step after this would be the European Central Bank which I joined in April 2016 and where I stayed for almost two years in the DG-Statistics. This time was incredibly challenging and enriching both from a professional perspective and a personal perspective due to my colleagues and the many great friendships I could make throughout this time. I want to mention in particular Francesca Gnecchi, Rocco Incardona, Matteo Paolo Pirone, Taja Sečnik, Simon Gollier, Laura Battalia, Nicolas Lemercier, Sara Thijs, Mattia Duma, Jörg Reddig, Sandrine Corvoisier, Peter Neudorfer, Riccardo Bonci, Gianluca Pallante, Jean-Marc Israel, Branchi Mariagnese, Marta Lopez Villa, Antonio Colangelo, Orestes Collazo Brananova, Catherine Ahsbahs, Alejandro Pica, Romana Peronaci, Alexandra-Iulia Chindea, Ioanna Kanioura, Julie Van Eeckhout, Me-Lie Yeh, Gemma Agostoni, Zeno Benetti, Damjan Strbac, Olgerd Unger, Darjan Divkovic, Bernadette Lauro, Krishanu Saha, Valeria Martone, Mirko de Giovanni, Sotorious Dimitrios Anagnostidis, Lyubomir Dilov, Nina Berghoff, Angelo Saponara, Johannes Micheler, Jürgen Herr and Sami Laiso.\\
\\
Soon after the ECB, I joined the amazing QAS-Team at EY Germany and, at the time of writing, am closing my second year. I will forever be grateful for the opportunity Dr. Bernhard Hein and Dr. Martin Dörr have given me to join their family at EY. I met wonderful people and learned an incredible amount about credit risk, market risk and the many challenges of banking in the 21st century. Thank you!